Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-11 doc/report/msc-report.tex
updated mapreduce section.

MapReduce is a framework for distributed computations on large data sets in
parallel across multiple clustered computers. It was inspired by the map and
reduce functions commonly found in functional programming languages.

As the name implies, MapReduce is made up of two parts or phases: map and
reduce. The map phase consumes one piece of input at a time (a piece of input
can be a line from a log file, for example), and emits an intermediate key and
value. These keys and values are then processed by the reduce phase, which emits
the final key-value pairs.

MapReduce works by splitting the input, which commonly is in the size
range of many gigabytes, into \textit{n} parts and lets each node of the
computing cluster work on one or more parts. The mapper on each node emits
key-value pairs which are fed into the reduce phase. The final output is
collated, usually on a distributed file system.

TODO: expand.
TODO: graph.

>>>>

MapReduce is a software framework for distributed computations on very large
data sets. The computations are run in parallel across a network of computers.

As the name implies, MapReduce is made up of two parts or phases: map and
reduce. The user specifies a map function that consumes a single key/value pair
to generate a set of intermediate key/value pairs, and a reduce function that
merges all intermediate values that belongs to the same key. The abstraction of
two functions to process skmall parts of the large data set was inspired by the
map and reduce functions commonly found in functional programming languages such
as Lisp. The use of this model allows the framework to easily parallelize the
computations. In the inevitable case of a failure at a computational node, the
computations that failed can simply be re-executed on another node.

MapReduce splits the input into \textit{n} pieces and assigns each computational
node of the cluster to work on one or more piece. The map function runs on each
node and emits key/value pairs. These are passed to the reduce function where
the values are collated by the reduce function.

[graphical element]
